Polytope notes

### 2020-01-24 notes/polytope-notes.tex
Using D(T) notation and rewriting notes and colt draft

  \section{Necessary and sufficient conditions for optimality}
  In this section, we have a collection of polytopes $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
  Given a vector $p \in \reals^n$ (for us, always a probability distribution), we write the $p$-weighted Minkowski sum of $\T^r$ as
    \[ \oplus_p \T^r := \left\{ \sum_{y \in \Y} p(y) x^r_y ~\Big|~ x^r_1 \in T^r_1, \dots, x^r_y \in T^r_y \right\} , \]
  in other words, the Minkowski sum of sets obtained by scaling each point in $T^r_y$ by $p(y)$.

  Recall the optimality condition:
  \begin{definition}[Optimality of subgradients for a level set]
    Given a collection of polytopes $\T^r = \{T_y^r \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \simplex$, the \emph{optimality condition $\Opt(\T^r, C)$ holds} if $p \in C \iff \vec{0} \in \oplus_p T^r$.
  \end{definition}

  Recall the main characterization theorem:
  \begin{theorem}
    Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} p \cdot \ell(r)\}$.
    Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$ such that both of the following hold:
    \begin{enumerate}
      \item (Optimality) For all $r \in \R$, we have $\Opt(\T^r, \gamma_r)$.
      \item (Monotonicity) (TODO)
    \end{enumerate}
  \end{theorem}

  \paragraph{Necessary conditions}
    With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Minkowski sum) holds, and these conditions are in relation to the support matrix $E$.

    \begin{condition}[Halfspace condition]\label{cond:H-condition}
    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T^r_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
    \end{condition}

  \paragraph{Sufficient conditions}
    Now in order to think about sufficient conditions for optimality, consider that convex polytopes all have $\V$-representations.
    Therefore, we can equivalently define the cell $C = \{p \in \simplex : Bp \geq \vec 0\} := \conv(\{p^1, \ldots, p^\ell\})$ for a finite set of distributions $p^j \in \simplex$, indexing with $j \in [\ell]$.
    Any distribution $p \in C$ can then be written as a convex combination of $p^j$ making up the convex hull.
%    , so $\vec 0$ being in those Minkowski sums implies that $\vec 0$ is also in the weighted Minkowski sum of any convex combination. \jessiet{Too hand wavy}
    \begin{condition}[Vertex condition]\label{cond:V-condition}
    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T^r$. %% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
    \end{condition}

  These two conditions together give us necessary and sufficient conditions for optimality.

  First, useful lemmas:
  \begin{lemma}  \label{lemma:minkowski-support-all}
    The condition $\vec 0 \in \oplus_p \T^r$ holds if and only if, for all $w \in \reals^d$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w,x} \geq 0$.
  \end{lemma}
  \begin{proof}
    Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
    In particular, by the halfspace representation of this set, $x \in \oplus_p \T^r$ if and only if, for all $w$, $\inprod{w}{x} \leq \max_{x' \in \oplus_p \T^r} \inprod{w}{x'}$.
    Now, $\max_{x' \in \oplus_p \T^r} \inprod{w}{x'} = \sum_y p(y) \max_{x' \in T^r_y} \inprod{w}{x'}$.
    Plugging in $x = \vec{0}$ completes the proof.
  \end{proof}
  \begin{lemma} \label{lemma:minkowski-support-finite}
    Given $\T^r$, there exists a finite collection $w_1,\ldots,w_K \in \reals^d$ for some $K$ such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $i \in [K]$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
  \end{lemma}
  \begin{proof}
    [Bo: TODO! The point: If we fix the support of $p$, there are only a finite number of normals that matter, regardless of which $p$ we pick. Varying over all finitely many choices of the support still gives a finite number of normals.]
  \end{proof}
  \begin{lemma} \label{lemma:E-to-B}
    Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
    Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
  \end{lemma}
  \begin{proof}
    [Bo: ?? We seem to use this above, but is there a citation?]
  \end{proof}

  \begin{theorem}\label{thm:nasc-optimality-conditions}
    $\Opt(\T^r, C)$ holds if and only if $\T^r$ and $C$ satisfy both the halfspace condition (\ref{cond:H-condition}) and the vertex condition (\ref{cond:V-condition}).
%  	Consider $B \in \reals^{k \times n}$ minimally describing $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\})$ for a given convex cell $C$.
%  	There exists $\T = \{T_1, \ldots, T_n\}$ such that $D^\T = C$ if and only if there exist normals $v_1, \ldots, v_k$, and points $x_{jy}$ such that the Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} hold.
  \end{theorem}
  \begin{proof}
    [Bo: rewritten, needs a look.]
    ($\implies$)
    First, we note that the vertex condition is immediately implied by $\Opt(\T^r,C)$.

    [Bo: feel this is a bit shaky where it cites $E$ and $B$ stuff.] To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use our construction to pick out the necessary vectors $v_1,\dots,v_k$.

    By Lemma \ref{lemma:minkowski-support-finite}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ where $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
    Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $0 \in \oplus_p \T^r \iff Ep \geq 0$.
    By assumption of $\Opt(\T^r,C)$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
    By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$. Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors $v_1,\ldots,v_k \in \reals^d$ with $\max_{x \in T^r_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.

    ($\impliedby$)
    The vertex condition gives that for all $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ such that $\vec 0 = \sum_y p^j(y) X^j_y$.
    Every $p \in C$ is a convex combination of $\{p^1,\ldots,p^{\ell}\}$, so taking the corresponding convex combination of the witnesses proves that $\vec 0 \in \oplus_p \T^r$.

    It remains to show that if $\vec 0 \in \oplus_p \T^r$, then $p \in C$.
    By Lemma \ref{lemma:minkowski-support-all}, $\vec 0 \in \oplus_p \T^r$ implies that for all $v$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{v}{x} \geq 0$.
    By the halfspace condition, there exist $v_1,\dots,v_k$ with $\max_{x \in T^r_y} \inprod{v_i}{x} \leq B_{iy}$, which implies $Bp \geq 0$, so $p \in C$.
    %% Bo: QED

%    Suppose $V^*$ is complete for $\T$.
%    Take $V = [v_1, \ldots, v_k]^T$ to be the normals corresponding to the nonredundant rows of $E$ with respect to $B$.
%    Each entry of the support matrix $E$ is equal to $B$ for these nonredundant normals by Proposition~\ref{prop:relate-rows}.
%    Therefore, Condition~\ref{cond:H-condition} is satisfied with the constructed set of normals $V$.    
%%    Condition~\ref{cond:H-condition} is satisfied by the existence of a halfspace representation of the polytopes $T_y$, which requires a superset $V^*$ of $V = [v_1, \ldots, v_k]^T$ such that $V^*$ is complete for $\T$ and reduction of redundant rows from the support matrix $E$, which make up $B$.
%    
%    Moreover, as $\{ p : Ep \geq \vec 0\} \subseteq \{p : Bp \geq \vec 0\}$ (since rows of $E$ are either in $B$ or redundant), we apply Lemma~\ref{lem:describe-D} to observe that there is a witness $x_y \in T_y$ for all $p \in D^\T$ such that $\oplus_y p_y x_y = \vec 0$, as this is a corollary of our optimality condition.
%    In particular, this is true for every distribution $p^j \in \{p^1, \ldots, p^\ell\}$, thus Condition~\ref{cond:V-condition} is satisfied.
%    
%    \bigskip
%    $\impliedby$
%    
%    Consider the set of polytopes $\T$ given so that there are normals $v_i$ and witnesses $x_{jy}$ satisfying Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition}.
%    With these polytopes, we want to show that $D^\T = C$.    
%
%    \bigskip
%    $D^\T \subseteq C$.
%    \bigskip
%    
%    We have $D^\T = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and $C = \{p \in \simplex : Bp \geq \vec 0\}$.
%    Take $p \not \in C$, and therefore $Bp < \vec 0$, and we will show $p \not \in D^\T$.
%    For some row $\bar i$ of $B$, we must have $\inprod{B_{\bar i}}{p} = b < 0$.
%    
%    By Condition~\ref{cond:H-condition}, we can write polytopes as $T_y = \{x : \inprod{v_i}{x} \leq B_{iy} \; \forall i \in [k]\}$, since the $max$ being equal $B_{iy}$ implies an inequality on all $x \in T_y$.
%    Moreover, by Theorem~\ref{thm:support-minksum}, we know the support of the weighted Minkowski sum is $Bp$, so the Minkowski sum can be written $\oplus_y p_y T_y = \{x : \inprod{v_i}{x} \leq (Bp)_i \; \forall i \in [k] \}$.
%    As $(Bp)_{\bar i} < 0$, we have that $\vec 0$ is not in $T(p)$, so we have $p \not \in D^\T$.
%    Thus, we have shown the contrapositive and have $D^\T \subseteq C$.
%    
%    \bigskip
%    $C \subseteq D^\T$.
%    \bigskip
%    
%    Take $p \in C$ so that $Bp \geq \vec 0$.
%    Observe that $D^\T$ is a convex polytope, as there is a complete set of normals $V^*$ for $\T$,\jessiet{haven't shown this in this doc, but doesld be easy enough to argue.} and we know that the support matrix $E$ can be constructed so that $D = \{p \in \simplex : Ep \geq \vec 0\}$, which is convex as it is the intersection of a finite number of halfspaces, bounded by simplex constraints, and closed by the weak inequality.
%%    it is bounded by simplex constraints, closed by definition, and convex by \jessie{ARGUE}.
%    By Condition~\ref{cond:V-condition}, we have that $p^1, \ldots, p^\ell$ are all in $D^\T$, since such witnesses imply $\vec 0$ is in the weighted Minkowski sum.
%    Moreover, as $C = \conv(\{p^1, \ldots, p^\ell\})$, we have $C \subseteq D^\T$.
%    
  \end{proof}

  \section{Quadratic program}
  Let us generalize our Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} into a quadratic feasibility program without given polytopes $\T$.

@@

  \begin{theorem}
  	Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T^r$ such that $\Opt(\T^r, C)$ if and only if there is a feasible solution to the above quadratic program.
  \end{theorem}
  \begin{proof}
    By Theorem \ref{thm:nasc-optimality-conditions}, it suffices to show that there exist $\T^r$ such that the halfspace and vertex conditions (\ref{cond:H-condition}, \ref{cond:V-condition}) hold if and only if the program is feasible.

>>>>

  \section{Necessary and sufficient conditions for optimality}
  In this section, we have a collection of polytopes $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
  Given a vector $p \in \reals^n$ (for us, always a probability distribution), we write the $p$-weighted Minkowski sum of $\T^r$ as
    \[ \oplus_p \T^r := \left\{ \sum_{y \in \Y} p(y) x^r_y ~\Big|~ x^r_1 \in T^r_1, \dots, x^r_y \in T^r_y \right\} , \]
  in other words, the Minkowski sum of sets obtained by scaling each point in $T^r_y$ by $p(y)$.
  Finally, we define $D(\T^r) = \{ p : \vec{0} \in \oplus_p \T^r\}$.

%  Recall the optimality condition:
%  \begin{definition}[Optimality of subgradients for a level set]
%    Given a collection of polytopes $\T^r = \{T_y^r \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \simplex$, the \emph{optimality condition $\Opt(\T^r, C)$ holds} if $p \in C \iff \vec{0} \in \oplus_p T^r$.
%  \end{definition}

  Recall the main characterization theorem:
  \begin{theorem}
    Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} p \cdot \ell(r)\}$.
    Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$ such that both of the following hold:
    \begin{enumerate}
      \item (Optimality) For all $r \in \R$, we have $D(\T^r) = \gamma_r$. %$\Opt(\T^r, \gamma_r)$.
      \item (Monotonicity) (TODO)
    \end{enumerate}
  \end{theorem}

  \begin{proposition} \label{prop:halfspace-opt}
    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
    Then $D(\T^r) \subseteq C$ if and only if there exist $v_1,\dots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
  \end{proposition}
  \begin{proof}
    ($\implies$)
    We are supposing that if $Bp \geq \vec{0}$, then $\vec{0} \in \oplus_p \T^r$.
    In particular, for all vectors $v \in \reals^d$, $0 \leq \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{v}{x}$.
    \bo{Not sure how to argue from here, unless we get into E matrix stuff. Raf?}

    ($\impliedby$)
    Let $p \in D(\T^r)$; we show $p \in C$.
    By definition, we have $\vec{0} \in \oplus_p \T^r$.
    This implies in particular that for each of the vectors $v_i$,
    \begin{align*}
      0 &\leq \max_{x \in \oplus_p \T^r} \inprod{v}{x}  \\
        &=    \sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{v_i}{x}  \\
        &\leq \sum_{y \in \Y} p(y) B_{iy} .
    \end{align*}
    This proves $Bp \geq 0$, so $p \in C$.
  \end{proof}

  \begin{proposition} \label{prop:vertex-opt}
    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\})$.
    Then $D(\T^r) \supseteq C$ if and only if $\vec 0 \in \oplus_{p^j} \T^r$ for all $j \in [\ell]$.
  \end{proposition}
  \begin{proof}
    ($\implies$)
    Because each $p^j \in C$, we have $p^j \in D(\T^r)$, and by definition, this gives $\vec{0} \in \oplus_{p^j} \T^r$.

    ($\impliedby$)
    Let $p \in C$; we show $p \in D(\T^r)$.
    For each $j$, there exist $\{X^j_y \in T^r_y : y \in \Y\}$ with $\vec{0} = \sum_{y \in \Y} p^j(y) X^j_y$.
    Write $p$ as a convex combination of $p^1,\ldots,p^{\ell}$.
    Let $x_y$ be the corresponding convex combination of $X^1_y,\ldots,X^{\ell}_y$.
    Because $X^1_y,\ldots,X^{\ell}_y \in T^r_y$, a convex set, so is $x_y$.
    And $\vec{0} = \sum_{y \in \Y} p(y) x_y$, so $p \in D(\T^r)$.
  \end{proof}

  \begin{corollary} \label{cor:vertex-halfspace-opt}
    Let the polytopes $\T^r = \{T^r_y \subseteq \reals^d : y \in \Y\}$ and $C$ be given, with $C = \conv(\{p^1,\ldots,p^{\ell}\}) = \{p: Bp \geq \vec 0\}$ for $B \in \reals^{k \times n}$.
    We have $D(\T^r) = C$ if and only if both of the following hold:
    \begin{enumerate}
      \item (Halfspace condition) There exist $v_1,\ldots,v_k \in \reals^d$ with $\inprod{v_i}{x} \leq B_{iy}$ for all $i \in [k], y \in \Y, x \in T^r_y$.
      \item (Vertex condition) For all $j \in [\ell]$, $\vec{0} \in \oplus_{p^j} \T^r$.
    \end{enumerate}
  \end{corollary}

%%  \paragraph{Necessary conditions}
%%    With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
%%    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Minkowski sum) holds, and these conditions are in relation to the support matrix $E$.
%%    
%%    \begin{condition}[Halfspace condition]\label{cond:H-condition}
%%    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \{p \in \simplex : Bp \geq \vec 0\}$ \emph{satisfy the halfspace condition} if there exist $v_1, \ldots, v_k \in \reals^d$ such that, for all $i \in [k]$ and $y \in \Y$, for all $x \in T^r_y$, we have $\inprod{v_i}{x} \leq B_{iy}$.
%%    \end{condition}
%%  
%%
%%  \paragraph{Sufficient conditions}
%%    Now in order to think about sufficient conditions for optimality, consider that convex polytopes all have $\V$-representations.
%%    Therefore, we can equivalently define the cell $C = \{p \in \simplex : Bp \geq \vec 0\} := \conv(\{p^1, \ldots, p^\ell\})$ for a finite set of distributions $p^j \in \simplex$, indexing with $j \in [\ell]$.
%%    Any distribution $p \in C$ can then be written as a convex combination of $p^j$ making up the convex hull.
%%%    , so $\vec 0$ being in those Minkowski sums implies that $\vec 0$ is also in the weighted Minkowski sum of any convex combination. \jessiet{Too hand wavy}
%%    \begin{condition}[Vertex condition]\label{cond:V-condition}
%%    	A collection of polytopes $\T^r$ and a polytope $C$ in the simplex defined by $C = \conv(\{p^1, \ldots, p^\ell\})$ \emph{satisfy the vertex condition} if for all $j \in [\ell]$, $0 \in \oplus_{p^j} \T^r$. %% Equivalent: there exist $\{x_{jy} \in T_y : j \in [\ell]\}$ such that, for all $j \in [\ell]$, $\sum_{y \in \Y} p^j_y x_{jy} = \vec 0$.
%%    \end{condition}
%%
%%  These two conditions together give us necessary and sufficient conditions for optimality.
%%
%%  First, useful lemmas:
%%  \begin{lemma}  \label{lemma:minkowski-support-all}
%%    The condition $\vec 0 \in \oplus_p \T^r$ holds if and only if, for all $w \in \reals^d$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w,x} \geq 0$.
%%  \end{lemma}
%%  \begin{proof}
%%    Recall by definition, the notation $\oplus_p \T^r = \{\sum_y p(y) x^r_y : x^r_y \in T^r_y (\forall y)\}$.
%%    In particular, by the halfspace representation of this set, $x \in \oplus_p \T^r$ if and only if, for all $w$, $\inprod{w}{x} \leq \max_{x' \in \oplus_p \T^r} \inprod{w}{x'}$.
%%    Now, $\max_{x' \in \oplus_p \T^r} \inprod{w}{x'} = \sum_y p(y) \max_{x' \in T^r_y} \inprod{w}{x'}$.
%%    Plugging in $x = \vec{0}$ completes the proof.
%%  \end{proof}
%%  \begin{lemma} \label{lemma:minkowski-support-finite}
%%    Given $\T^r$, there exists a finite collection $w_1,\ldots,w_K \in \reals^d$ for some $K$ such that $\vec 0 \in \oplus_p \T^r$ if and only if, for all $i \in [K]$, $\sum_{y \in \Y} p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
%%  \end{lemma}
%%  \begin{proof}
%%    [Bo: TODO! The point: If we fix the support of $p$, there are only a finite number of normals that matter, regardless of which $p$ we pick. Varying over all finitely many choices of the support still gives a finite number of normals.]
%%  \end{proof}
%%  \begin{lemma} \label{lemma:E-to-B}
%%    Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
%%    Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
%%  \end{lemma}
%%  \begin{proof}
%%    [Bo: ?? We seem to use this above, but is there a citation?]
%%  \end{proof}
%%
%%  \begin{theorem}\label{thm:nasc-optimality-conditions}
%%    $\Opt(\T^r, C)$ holds if and only if $\T^r$ and $C$ satisfy both the halfspace condition (\ref{cond:H-condition}) and the vertex condition (\ref{cond:V-condition}).
%%%  	Consider $B \in \reals^{k \times n}$ minimally describing $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\})$ for a given convex cell $C$.
%%%  	There exists $\T = \{T_1, \ldots, T_n\}$ such that $D^\T = C$ if and only if there exist normals $v_1, \ldots, v_k$, and points $x_{jy}$ such that the Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} hold.
%%  \end{theorem}
%%  \begin{proof}
%%    [Bo: rewritten, needs a look.]
%%    ($\implies$)
%%    First, we note that the vertex condition is immediately implied by $\Opt(\T^r,C)$.
%%
%%    [Bo: feel this is a bit shaky where it cites $E$ and $B$ stuff.] To show the halfspace condition is satisfied, we first construct a matrix $E$ such that $Ep \geq 0 \iff Bp \geq 0$, then use our construction to pick out the necessary vectors $v_1,\dots,v_k$.
%%
%%    By Lemma \ref{lemma:minkowski-support-finite}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ where $\vec 0 \in \oplus_p \T^r$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{w_i}{x} \geq 0$.
%%    Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T^r_y} \inprod{w_i}{x}$, and we have $0 \in \oplus_p \T^r \iff Ep \geq 0$.
%%    By assumption of $\Opt(\T^r,C)$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
%%    By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$. Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors $v_1,\ldots,v_k \in \reals^d$ with $\max_{x \in T^r_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.
%%
%%    ($\impliedby$)
%%    The vertex condition gives that for all $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ such that $\vec 0 = \sum_y p^j(y) X^j_y$.
%%    Every $p \in C$ is a convex combination of $\{p^1,\ldots,p^{\ell}\}$, so taking the corresponding convex combination of the witnesses proves that $\vec 0 \in \oplus_p \T^r$.
%%
%%    It remains to show that if $\vec 0 \in \oplus_p \T^r$, then $p \in C$.
%%    By Lemma \ref{lemma:minkowski-support-all}, $\vec 0 \in \oplus_p \T^r$ implies that for all $v$, $\sum_y p(y) \max_{x \in T^r_y} \inprod{v}{x} \geq 0$.
%%    By the halfspace condition, there exist $v_1,\dots,v_k$ with $\max_{x \in T^r_y} \inprod{v_i}{x} \leq B_{iy}$, which implies $Bp \geq 0$, so $p \in C$.
%%    %% Bo: QED
%%
%%    
%%%    Suppose $V^*$ is complete for $\T$.
%%%    Take $V = [v_1, \ldots, v_k]^T$ to be the normals corresponding to the nonredundant rows of $E$ with respect to $B$.
%%%    Each entry of the support matrix $E$ is equal to $B$ for these nonredundant normals by Proposition~\ref{prop:relate-rows}.
%%%    Therefore, Condition~\ref{cond:H-condition} is satisfied with the constructed set of normals $V$.    
%%%%    Condition~\ref{cond:H-condition} is satisfied by the existence of a halfspace representation of the polytopes $T_y$, which requires a superset $V^*$ of $V = [v_1, \ldots, v_k]^T$ such that $V^*$ is complete for $\T$ and reduction of redundant rows from the support matrix $E$, which make up $B$.
%%%    
%%%    Moreover, as $\{ p : Ep \geq \vec 0\} \subseteq \{p : Bp \geq \vec 0\}$ (since rows of $E$ are either in $B$ or redundant), we apply Lemma~\ref{lem:describe-D} to observe that there is a witness $x_y \in T_y$ for all $p \in D^\T$ such that $\oplus_y p_y x_y = \vec 0$, as this is a corollary of our optimality condition.
%%%    In particular, this is true for every distribution $p^j \in \{p^1, \ldots, p^\ell\}$, thus Condition~\ref{cond:V-condition} is satisfied.
%%%    
%%%    \bigskip
%%%    $\impliedby$
%%%    
%%%    Consider the set of polytopes $\T$ given so that there are normals $v_i$ and witnesses $x_{jy}$ satisfying Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition}.
%%%    With these polytopes, we want to show that $D^\T = C$.    
%%%
%%%    \bigskip
%%%    $D^\T \subseteq C$.
%%%    \bigskip
%%%    
%%%    We have $D^\T = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and $C = \{p \in \simplex : Bp \geq \vec 0\}$.
%%%    Take $p \not \in C$, and therefore $Bp < \vec 0$, and we will show $p \not \in D^\T$.
%%%    For some row $\bar i$ of $B$, we must have $\inprod{B_{\bar i}}{p} = b < 0$.
%%%    
%%%    By Condition~\ref{cond:H-condition}, we can write polytopes as $T_y = \{x : \inprod{v_i}{x} \leq B_{iy} \; \forall i \in [k]\}$, since the $max$ being equal $B_{iy}$ implies an inequality on all $x \in T_y$.
%%%    Moreover, by Theorem~\ref{thm:support-minksum}, we know the support of the weighted Minkowski sum is $Bp$, so the Minkowski sum can be written $\oplus_y p_y T_y = \{x : \inprod{v_i}{x} \leq (Bp)_i \; \forall i \in [k] \}$.
%%%    As $(Bp)_{\bar i} < 0$, we have that $\vec 0$ is not in $T(p)$, so we have $p \not \in D^\T$.
%%%    Thus, we have shown the contrapositive and have $D^\T \subseteq C$.
%%%    
%%%    \bigskip
%%%    $C \subseteq D^\T$.
%%%    \bigskip
%%%    
%%%    Take $p \in C$ so that $Bp \geq \vec 0$.
%%%    Observe that $D^\T$ is a convex polytope, as there is a complete set of normals $V^*$ for $\T$,\jessiet{haven't shown this in this doc, but doesld be easy enough to argue.} and we know that the support matrix $E$ can be constructed so that $D = \{p \in \simplex : Ep \geq \vec 0\}$, which is convex as it is the intersection of a finite number of halfspaces, bounded by simplex constraints, and closed by the weak inequality.
%%%%    it is bounded by simplex constraints, closed by definition, and convex by \jessie{ARGUE}.
%%%    By Condition~\ref{cond:V-condition}, we have that $p^1, \ldots, p^\ell$ are all in $D^\T$, since such witnesses imply $\vec 0$ is in the weighted Minkowski sum.
%%%    Moreover, as $C = \conv(\{p^1, \ldots, p^\ell\})$, we have $C \subseteq D^\T$.
%%%    
%%  \end{proof}

  \section{Quadratic program}

@@

  \begin{theorem}
  	Given a convex polytope $C \subseteq \simplex$, there exist polytopes $\T^r$ in dimension $d$ such that $D(\T^r) = C$ if and only if there is a feasible solution to the above quadratic program with parameter $d$.
  \end{theorem}
  \begin{proof}
    By Corollary \ref{cor:vertex-halfspace-opt}, it suffices to show that $\T^r$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
